
\begin{center}
    \Huge
    Vasilii Matrenin \\
    \Large
    C/C++ Developer
\end{center}

\vspace* {0.6cm}

\begin{minipage}[t]{12cm}

\subsection* {Projects}
\begin{itemize}

\item \textbf {Bachelors second-year projects:} \\ [0.1cm]
    There is $\href {https://github.com/VasiliyMatr/ILAB_2ndYEAR}{repository}$
    with my Intel ILAB projects. There are good projects written in C++ and built with
    CMake in this repository.

    GitHub: VasiliyMatr/ILAB\_2ndYEAR .

\item \textbf {Bachelors first-year projects:} \\ [0.1cm]
    There are two repositories with my bachelors first-year projects:

    First-term $\href {https://github.com/VasiliyMatr/MIPT_PROG_1stTERM}{repository}$
    - With interesting toy programming language compiler
    $\href {https://github.com/VasiliyMatr/MIPT_PROG_1stTERM/tree/master/T08LANG}{T08}$
    and CPU simulator
    $\href {https://github.com/VasiliyMatr/MIPT_PROG_1stTERM/tree/master/T04CPU}{T04}$
    which executes compiler outputs. There are also other interesting projects.

    GitHub: VasiliyMatr/MIPT\_PROG\_1stTERM . \\ [0.1cm]

    Second-term $\href {https://github.com/VasiliyMatr/MIPT_PROG_2ndTERM}{repository}$
    - With optimization projects
    $\href {https://github.com/VasiliyMatr/MIPT_PROG_2ndTERM/tree/master/T05MANDEL}{T05}$ ,
    $\href {https://github.com/VasiliyMatr/MIPT_PROG_2ndTERM/tree/master/T06HASH}{T06}$;
    assembly tryouts and there is also T04CPU executable files to x86 executable files translator -
    $\href {https://github.com/VasiliyMatr/MIPT_PROG_2ndTERM/tree/master/T07JIT}{T07}$.

    GitHub: VasiliyMatr/MIPT\_PROG\_2ndTERM .

\end{itemize}

\end{minipage}
\begin{minipage}[t]{6.5cm}

\subsection* {My skills}
\begin{itemize}
    \item \textbf{C/C++} \\
    \item Good practice skills in \textbf{CMake} and \textbf{Make}. \\
    \item Advanced \textbf{CPU architecture} knowledge. \\
    \item Basic skills in \textbf{Bash}. \\
    \item B1 \textbf{English} level. \\
    \item Good practice skills in \textbf{Tex}. \\
    \item Basic skills in \textbf{Python}. \\

\end{itemize}

\end{minipage}

\subsection* {Working experience}
I have worked in Intel corporation as a summer intern for two months. My manager and mentor
highly valued my work and sent good
$\href {https://github.com/VasiliyMatr/CV/tree/master/PDF/ISI2021_feedback.pdf}{feedback}$.

\subsection* {Higher education}
Second-year bachelors student in MIPT; Department of Radio Engineering and
Cybernetics (DREC); Applied physics and mathematics.

\subsection* {Completed additional courses}
\begin{itemize}
    \item Industrial programming cource - during bachelors first-year in MIPT. \\
    Lecturer - I. Dedinsky.
    \item HiSilicon OS and CPU simulation cource - during bachelors second-year in MIPT. \\
    Lecturer - I. Petushkov.
    \item Intel ILAB C++ cource - during bachelors second-year in MIPT. \\
    Lecturer - K. Vladimirov.
    \item Intel ILAB micro architecture cource - during bachelors second-year in MIPT. \\
    Lecturer - K. Korolev. \\

    \item DREC microcontrollers course.
    \item DREC FPGA course.
\end{itemize}
